HO unification from object language to meta language

### 2024-03-27 paper/main.tex
update compil of eta

\begin{invariant}[Link left hand side]\label{inv:linklhs}
  The left hand side of a suspended link
  is a variable.
\end{invariant}

\noindent
New links are suspended by construction.
If the left hand side variable is assigned during a step, then 
the link is considered for progress and possibly eliminated.
This is discussed in \cref{sec:eta} and \cref{sc:beta}.

@@

\noindent
Note tha the infix notation \elpiIn{((A ~\Ue~B) C D)} is syntactic sugar for
\elpiIn{((~\Ue\!\!\!~) A B C D)}.

@@

Since compilation moves problematic terms out of the compiled terms,
\Ue{} can only perform a partial occur check. For example the
unification problem $X \Ue f~Y$ cannot generate a cyclic substitution alone,
but should be disallowed if a $\linkStore$ contains a link like
$\linketaM{}{Y}{\lambda z.X_z}$: We don't know yet if $Y$ will feature
a lambda in head position, but we surely know it contains $X$, hence
$f~Y$ and that triggers occur check.
The procedure \elpiIn{occur-check-links} is in charge of ensuring that
each link does not represent a (suspended) unification problem doomed
to fail because of occur check. This check is needed in order to
guarantee \cref{prop:fidelity} (simulation fidelity).

>>>>

\begin{invariant}[Link left hand side]\label{inv:linklhs}
  The left hand side of a new link
  is a variable.
\end{invariant}

\noindent
If the variable is assigned during a run the link is considered for
progress and possibly eliminated. This is discussed in
section~\ref{sec:eta}.\marginpar{is this the right section?}

@@

\noindent
Note tha the notation \elpiIn{((A ~\Ue~B) C D)} is syntactic sugar for
\elpiIn{((~\Ue~) A B C D)}.

@@

TODO: discuss occur check
